\section{Introduction}
 This section is used for multiple kinds of documents.  It describes the
 purpose of this document in the context of the rest of the product's
 documentation library.  

\subsection{Purpose}
The purpose of this software requirement specifications document is to outline the functional and nonfunctional requirements for the PACCAR wire validation project. This document is intended to be used by the Western development team to outline project requirements before implementation

\subsection{Document Conventions}

 The use of the plural shall imply singular unless stated otherwise.
 

\subsection{Intended Audience and Reading Suggestions}
 This document was created for use by the team in designing software requirements. We have designed this document using layman terminology so no outside readings are required for understanding the domain. Readers should have a basic idea of the contents of a wiring diagram.

\subsection{Project Scope}
PACCAR designs and builds highly customizable trucks for their clients. Organizing multiple wire schematics in order to validate the design of the electrical components of the truck is a time-consuming task. This project will read the wiring diagrams for a truck, organize the data about each wire, and provide a streamlined output for easier validation of the components and wiring of the truck.

\subsection{References}
 Readers should reference the Vision and Scope document for this project for a more detailed overview of the project scope.
